Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: use Ref.~\citenum{} for inline numbers

The line of arguments used above assumes neutral solvent species and
thus is not directly applicable to electrolytes. However, even then
the behavior at low $k$ of a convolution like in Eq.~\ref{eq:tau}
can be assumed to be regular; see the discussion of the background
charge correction in Ref.~\citep{Kovalenko00b}. Indeed, a physically
viable electrolyte model with a suitable susceptibility $\chi$ is
intuitively expected to reproduce charge screening at finite Debye
length. Then the convolution $h\sim-\chi\ast v_{\text{L}}$, interpreted
here as a first-order response of the solvent distribution to an electrostatic
field $v_{\text{L}}$, cf.~Eqs.~\ref{eq:rsim-h-c-t}, also decays
at that same length scale \citep{Kovalenko00b}.

@@

\raggedright{}$^{a}$~Energies in kcal/mol. KH and HNC closure relations
have been used. 3D domain of $20^{3}$~Å$^{3}$, grid of $64^{3}$~points.
$^{b}$~Ref.~\citep{Bo15}. $^{c}$~MD with SPC/E water; Ref.~\citep{Joung08}.
$^{d}$~Ref.~\citep{Schmid00}. 
\end{table*}

@@

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3 (solid lines of decreasing weight). The dashed line
represents the MD result of Ref.~\citep{Bo15}.
\label{fig:potential-of-mean-force}}

>>>>

The line of arguments used above assumes neutral solvent species and
thus is not directly applicable to electrolytes. However, even then
the behavior at low $k$ of a convolution like in Eq.~\ref{eq:tau}
can be assumed to be regular; see the discussion of the background
charge correction in Ref.~\citenum{Kovalenko00b}. Indeed, a physically
viable electrolyte model with a suitable susceptibility $\chi$ is
intuitively expected to reproduce charge screening at finite Debye
length. Then the convolution $h\sim-\chi\ast v_{\text{L}}$, interpreted
here as a first-order response of the solvent distribution to an electrostatic
field $v_{\text{L}}$, cf.~Eqs.~\ref{eq:rsim-h-c-t}, also decays
at that same length scale \citep{Kovalenko00b}.

@@

\raggedright{}$^{a}$~Energies in kcal/mol. KH and HNC closure relations
have been used. 3D domain of $20^{3}$~Å$^{3}$, grid of $64^{3}$~points.
$^{b}$~Ref.~\citenum{Bo15}. $^{c}$~MD with SPC/E water; Ref.~\citenum{Joung08}.
$^{d}$~Ref.~\citenum{Schmid00}. 
\end{table*}

@@

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3 (solid lines of decreasing weight). The dashed line
represents the MD result of Ref.~\citenum{Bo15}.
\label{fig:potential-of-mean-force}}
